### Question 2

Calculate the crude and graduated estimates of mortality rate.

To estimate mortality rate, use Binomial model. Calculate the standardised deviation z score.

```{r}
Ex<-c(15518,19428,21594,21890,19174,15775,11414,6993,3276,1096,201)
actualdeath<-c(65,144,219,378,465,557,685,644,471,217,67)
expecteddeath<-c(73.9,134.6,223.9,346.3,468.1,600.2,675.5,637.4,458.7,240.6,61.4)

crudeqx<-actualdeath/Ex
graduatedqx<-expecteddeath/Ex
zx<-(actualdeath-expecteddeath)/sqrt(expecteddeath*(1-graduatedqx))
zx
```

#### (a) chi-squared test

$$\sum_{allages}{z_x^2}$$

Using chi square test to check whether graduated estimates are close to data. Calculate the sum of z score square.

The result is smaller than the value of $\chi^2(0.95)$ .Degree of freedom is 10. Therefore, null hypothesis is not rejected and adherence to data is good.

```{r}
zx2<-(zx)^2
CST<-sum(zx2)
CST
qchisq(0.95,10)
```

#### (b) standard deviations test

$$\sum_{allages}\frac{(A-E)^2}E$$

Divide the 11 z score in 4 intervals, using standard deviations test.

The result is smaller than the value of $\chi^2(0.95)$ .Degree of freedom is 3. Therefore, null hypothesis is not rejected and adherence to data is good.

```{r}
c=data.frame(zx)
Ainterval1<-length(c[c$zx<(-1),1])
Ainterval2<-length(c[c$zx<0&c$zx>-1,1])
Ainterval3<-length(c[c$zx<1&c$zx>0,1])
Ainterval4<-length(c[c$zx>1,1])
A<-c(Ainterval1,Ainterval2,Ainterval3,Ainterval4)
E<-11*c(pnorm(-1),pnorm(0)-pnorm(-1),pnorm(1)-pnorm(0),1-pnorm(1))
SDT<-sum((A-E)^2/E)
SDT
qchisq(0.95,3)
```

#### (c) Cumulative Deviations Test

$$\frac{\sum_x(d_x-Exq_x)}{\sqrt{\sum_x{Exqx(1-q_x)}}}$$

The of absolute value of result is smaller than 1.96. Therefore, null hypothesis is not rejected and adherence to data is good.

```{r}
CDT<-abs(sum(actualdeath-expecteddeath)/sqrt(sum(expecteddeath*(1-graduatedqx))))
CDT
qnorm(0.975)
```

#### (d) Signs Test

The number of positive z score should be Binomial distributed. Doing binomial test and the p value is 1, which is larger than 0.05. Null hypothesis is not rejected and is a Binomial distribuion.

Meanwhile, calculate smallest possible value k. The number of positive z score is smaller than m ¨C k and larger than k, so the adherence to data is good.

```{r}
ST<-length(c[c$zx> 0,1])
ST
k<-qbinom(0.025,11,0.5)
k
binom.test(ST,11,0.5,"two.sided")
```

#### (e) Grouping of Signs Test

It is oberved that the number of distinct groups of positive z score is 4. Calculate the smallest possible value k. The number of distinct groups of positive z score is larger than k, z score is standard normal, so null hypothesis is not rejected and adherence to data is good.

```{r}
n=4
n
n1<-length(c[c$zx> 0,1])
n2<-length(c[c$zx< 0,1])
fn<-function(j){sum(choose(n1-1,j-1)*choose(n2+1,j)/choose(n1+n2,n1))}

temp<-fn(1)
for (j in 1:11) {
  if(temp<0.05){
    temp<-temp+fn(j)  
  }else{
    break("")
  }
}
j
```

#### (f) Serial Correlations Test

The absolute value of result is smaller than 1.96. Therefore, null hypothesis is not rejected and adherence to data is good.

```{r}
z1<-sum(zx[1:10]/(11-1))
z2<-sum(zx[2:11]/(11-1))
SCT<-abs(sum((zx[1:10]-z1)*(zx[2:11]-z2))*sqrt(11-1)/sqrt(sum((zx[1:10]-z1)^2)*(sum((zx[2:11]-z2)^2))))
SCT
qnorm(0.975)
```