### Question 3

#### Example 5.7

To calculate the force of mortality, using the Poisson model. Set the loglikelihood function. 

For  Gompertz¡¯ Law, $\mu=Bc^x$

Obtain the start point of b and c through linear regression. 

Find the minimized value of the function to obtain the value of b and c.Then obtain the graduated estimates of force of mortality.

```{r}
age<-seq(70,75,1)
ECx<-c(1000,1005,1010,1008,1006,998)
dx<-c(80,90,95,105,115,125)
crude<-dx/ECx

fn<-function(theta){
  -sum(-ECx*theta[1]*theta[2]^age+dx*log(ECx*theta[1]*(theta[2]^age)))
  }
  
  
lm(log(crude)~age)
b1<-exp(-8.67325)
c1<-exp(0.08788)
b1
c1

estimate<-nlm(fn,c(b1,c1))
b<-estimate$estimate[1]
c<-estimate$estimate[2]

mu<-b*c^age
mu
```



#### Example 5.8

To calculate the force of mortality, using the Binomial model.

Calculate the crude estimates of q.

Set th function. The weight is the initial exposed to risk.

Obtain the start point of a and b through linear regression. 

Find the minimized value of the function to obtain the value of b and c.Then obtain the graduated estimates of mortality rate.

```{r}
age<-seq(30,49,1)
Ex<-c(70000,66672,68375,65420,61779,66091,68514,69560,65000,66279,
      67300,65368,65391,62917,66537,62302,62145,63856,61097,61110)
dx<-c(39,43,34,31,23,50,48,43,48,47,
      62,63,84,86,120,121,122,162,151,184)
crudeqx<-dx/Ex
Wx<-Ex

fn<-function(theta){sum(Wx*(log(crudeqx/(1-crudeqx))-(theta[1]+theta[2]*age))^2)}

lm(log(crudeqx/(1-crudeqx))~age)
a1<--10.8629
b1<-0.1003

estimate<-nlm(fn,c(a1,b1))
estimate
a<-estimate$estimate[1]
b<-estimate$estimate[2]

graduatedqx<-exp(a+b*age)/(1+ exp(a+b*age))
graduatedqx

```

#### Exmple 5.9

To calculate the force of mortality, using the Binomial model.

Calculate the crude estimates of q.

Set th function. The weight is the initial exposed to risk.

Obtain the start point of a and b through linear regression. 

Find the minimized value of the function to obtain the value of b and c.Then obtain the graduated estimates of mortality rate.

```{r}
Ex<-c(166,187,218,243,276,302,347,
      390,430,494,558,628,701,813,
      917,1040,1182,1299,1432,1596,1752)
dx<-c(2,2,4,6,2,4,7,
      3,9,9,8,11,14,18,
      18,24,30,43,41,54,64)
qSx<-c(0.00505,0.00570,0.00644,0.00728,0.00826,0.00930,0.01051,
       0.01184,0.01331,0.01492,0.01668,0.01859,0.02065,0.02287,
       0.02525,0.02778,0.03049,0.03339,0.03648,0.03978,0.04332)
crudeqx<-dx/Ex
Wx<-Ex

fn <- function(theta){sum(Wx*(crudeqx-(theta[1]+theta[2]*qSx))^2)}

lm(crudeqx~qSx)
a1<-0.009279
b1<-0.570217

estimate<-nlm(fn,c(a1,b1))
estimate

a<-estimate$estimate[1]
b<-estimate$estimate[2]

graduatedqx<-a+b*qSx
graduatedqx
  
```
